MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-04-19 MAESTROeX_I/results.tex
add results for long wdconvect runs until ignition

Reacting bubble simulation at effective resolution of $128^2 \times 1024$ run on Cori Haswell with 48 processors took 33.54 s per time step (averaged over 10 time steps) to run on single-level grid and only 3.70 s on adaptive grid with two levels of refinement. This 89\% decrease in runtime is mostly due to the fact that only 6.25\% of the cells (1,048,576 out of $128^2 \times 1024$ cells) are refined at the the finest level for the AMR run.

\subsection{White Dwarf Convection}
white dwarf convection runs with 3 algorithms (original, new temporal, new temporal + irregular base state)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=3.5in]{./figs/wdconvect_amr_Tmax} 
\caption{\label{fig:wdconvect_amr_Tmax} Peak temperature, $T_{\text{peak}}$, in a white dwarf from $t=0$ to $350$ s  
for grids with effective resolution of $256^3$. We can see that the adaptive grids with two levels of refinement 
give very similar solution trends compared to the single-level grid.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Reacting bubble simulation at effective resolution of $128^2 \times 1024$ run on Cori Haswell with 48 processors took approximately 33.5 s per time step (averaged over 10 time steps) to run on single-level grid using either the original or new temporal algorithm, and only 3.7 s on adaptive grid with two levels of refinement. This 89\% decrease in runtime is mostly due to the fact that only 6.25\% of the cells (1,048,576 out of $128^2 \times 1024$ cells) are refined at the the finest level for the AMR run.

\subsection{White Dwarf Convection}

white dwarf convection runs with 3 algorithms (original, new temporal, new temporal + irregular base state)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=2.75in]{./figs/wdconvect_128_maxT} 
\includegraphics[width=2.75in]{./figs/wdconvect_128_maxMach}
\caption{\label{fig:wdconvect_128_maxval} (left) Peak temperature, $T_{\text{peak}}$, and (right) peak Mach number 
         in a white dwarf until time of ignition at resolution of $128^3$ for three different MAESTROeX algorithms.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=3.5in]{./figs/wdconvect_amr_Tmax} 
\caption{\label{fig:wdconvect_amr_Tmax} Peak temperature, $T_{\text{peak}}$, in a white dwarf from $t=0$ to $350$ s 
         for grids with effective resolution of $512^3$. We can see that the adaptive grids with two levels of 
         refinement give very similar solution trends compared to the single-level grid.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
